Topic models

### 2021-02-11 topic_models.Rmd
LDA output format md

---
title: "Topic models"
author: "Caspar J. van Lissa"
date: "2/10/2021"
output:
  bookdown::html_document2:
    number_sections: false
bibliography      : ["veni_sysrev.bib"]
---

```{r setup, include=FALSE}
library(yaml)
knitr::opts_chunk$set(echo = TRUE)
lda_dims <- read_yaml("Study1_lda_dims.txt")
dtm_top <- read_yaml("study1_dtm_top.yml")
df <- readRDS("study1_df.RData")
number_docs_words <- yaml::read_yaml("study1_number_docs_words.txt")
```

>>>>

---
title: "Topic models"
author: "Caspar J. van Lissa"
date: "2/10/2021"
output:
  bookdown::github_document2:
    number_sections: false
bibliography      : ["veni_sysrev.bib"]
---

```{r setup, include=FALSE}
library(yaml)
knitr::opts_chunk$set(echo = FALSE)
lda_dims <- read_yaml("Study1_lda_dims.txt")
dtm_top <- read_yaml("study1_dtm_top.yml")
df <- readRDS("study1_df.RData")
number_docs_words <- yaml::read_yaml("study1_number_docs_words.txt")
```
